The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
improve atompub start
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@217 43ef1190-90fd-4dd7-a769-d0121f02b80e
new h factors
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@218 43ef1190-90fd-4dd7-a769-d0121f02b80e

% TODO:
% Explain HATEOAS
% More on new H-factors
% References
% POST in relation to graph store
% Weakness of RDF
% Reformulate something on SPARQL about enabling

@@

% TODO: rough start
AtomPub has a single service endpoint, and you can navigate to what
you need from there. This motivates the first discussion topic of this
paper:

@@

\begin{itemize}
\item Support for supplying control data relevant to subsequent requests.

@@

\item A factor for RaUL templates.

The RaUL\footnote{\url{http://vocab.deri.ie/raul}} goes beyond HTTP
GET queries, but can be used to formulate templated queries similar to
those in HTML, or indeed to generate HTML fragments for the same purpose.

>>>>

% TODO:
% References
% POST in relation to graph store
% Weakness of RDF
% Reformulate something on SPARQL about enabling
% More writing around factors?

@@

AtomPub %TODO: ref
is a widely cited as a good example of a RESTful protocol and
we note that it has a single service endpoint. From there, you can
navigate to what you need. This motivates the first discussion topic
of this paper:

@@

Mike Amundsen solicits feedback on the completeness of his
classification scheme. I suggest the following as discussion items:

\begin{itemize}

The self-describing nature of RDF is an important characteristic of
the model and arguably an important characteristic of RDF as
hypermedia as agents may be able to infer possible interactions based
on vocabulary definitions.

\item Support for supplying control data relevant to subsequent requests.

It may be useful for agents to know e.g. what formats they can send to
a given resource before the request is made. This may require a new
control data factor. An example of this use may be e.g.:

@@

\item A factor encompassing RaUL templates.

  The RaUL\footnote{\url{http://vocab.deri.ie/raul}} goes beyond HTTP
  GET queries, which is what the \textsf{LT} factor is about, but can
  be used to formulate templated queries similar to those in HTML, or
  indeed to generate HTML fragments for the same purpose. This is also
  enables useful interactions, albeit quite different from those of
  this paper.
